Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-19 journal/article.tex
Large scale

--> Needs to have complexity in software design?? --> What is complexity in software?
    Is ``complexity'' an issue in agile?
    What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
--> Formal definitions (EU, etc.) look at project costs or company turnover.
    These definitions do not take a standpoint on complexity of the product, so
    they do not matter in the context of SDMs.

>>>>

--> What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.
